---
title: "README"
author: "Anthony Tedde"
date: "October 19, 2017"
output: html_document
---


## Random Walk package (RandomWalk)

The aim of this package is to provide a way to create and manipulate random walk according to its properties.

# Load the package

```{r load, echo=TRUE}
library(RandomWalk)
```


## Function provided by the package

* adaptedSampledRandomWalkGenerator
* adaptedSampledRandomWalk
* sampleRandomWalk
* sampleRandomWalkGenerator
  

## Function and arguments

 
> adaptedSampledRandomWalkGenerator

Function that return a list of data.frame.
Each data.frame contains two variables. 

The first one is the x label (which correspond to the index of the adapted 
filtration)

The second column is a sampled symmetric random walk.
There are as many path as the value of argument **n**. 

For instance the following code: 

```{r}
library(RandomWalk)
adaptedSampledRandomWalkGenerator(steps = 500, n = 20)
```

will generate a list of **20** random walks along with the index of each step.

| Argument | Description |
|---|---|
| steps | Number of steps of the random walk |
| prob | Probability of occurence of head and tails for each step |
| n | Number of random walk generated by the function |

> adaptedSampledRandomWalk

| Argument | Description |
|---|---|
| steps | Number of steps of the random walk |
| prob | Probability of occurence of head and tails for each step |

> sampleRandomWalkGenerator

| Argument | Description |
|---|---|
| steps | Number of steps of the random walk |
| prob | Probability of occurence of head and tails for each step |
| n | Number of random walk generated by the function |

> sampleRandomWalk

| Argument | Description |
|---|---|
| steps | Number of steps of the random walk |
| prob | Probability of occurence of head and tails for each step |

