# Random Walk R package (RandomWalk)

The aim of this package is to provide a way to create and manipulate simple random walk and brownian motion  or array of them. I would be noticed that the calculation
of brownian motion is made by taking the limit of the random walk as its steps size
goes to zero. The brownian motion could therefore be read as a continously stepped
random walk.

All caluculation could be made according to their properties. Among these available:

* Expectation and variance of random walk/brownian motion
* Expectation and variance of increments
* Quadratic variation (source of the volatility computed path by path, where
probabilities is not taken into account.)

(!) Quadratic variation should be seen as the volatility term of a random walk/
brownian motion.

## Load the package

```{r load, echo=TRUE}
library(RandomWalk)
```

## Functions provided by the package

* Multiple sampled radom walk generator: [srwalkGenerator](#srwalkgenerator)
* Sampled radom walk constructor: [srwalk](#srwalk)
* Theoretical radom walk: [trwalk]
* Quadratic variation: [qvar]
* Expectation of radom walk/brownian motion: [rwexp]
* Expectation of increments: [iexp]
* Variance of radom walk/brownian motion: [rwvar]
* Variance of increments: [ivar]
 
## Description of the functions as they was created and defined

The following lines does not give example of usage of the package functions.
<!-- To get a useful bunch of way.. One can refers to "Example" folder. -->
Instead of giving such examples, they provide an brief description of the arguments 
the package functions take as well as the way these agruments are defined (along
with the default value they take)

```{r}
srwalkGenerator(steps = 100,
                prob = c('head' = .5, 'tail' = .5),
                scale = 1,
                n = 1)

srwalk(steps = 3000,
       prob = c('head' = .5, 'tail' = .5),
       scale =1)
```
  
## Functions and arguments 
 
### srwalkGenerator

| Arguments | Description |
|---|---|
| steps | Number of steps of the random walk |
| prob | Probability of occurence of head and tails for each step |
| scale |  |
| n | Number of random walk generated by the function |

This function return a R [list](https://www.rdocumentation.org/packages/base/versions/3.4.1/topics/list)
of multiple [data.frame](https://www.rdocumentation.org/packages/base/versions/3.4.1/topics/data.frame)s,
with each one containing:

1. *x axis*: Ordered vector from 0 up to T. It represents the time period in which the random walk evolved.
2. *y axis*: All random values taken by the symmetric sampled random walk. This variable depends on the time
independent non-random variable

#### Example of usage of adaptedSampledRandomWalkGenerator function:

```{r}
library(RandomWalk)
# The following line set the variable @sampled with a list of 20
# data.frame of Adapted random walk.
Sampled <- adaptedSampledRandomWalkGenerator(steps = 500, n = 20)
```

### srwalk

| Arguments | Description |
|---|---|
| steps | Number of steps of the random walk |
| prob | Probability of occurence of head and tails for each step |

It return a unique adapted sampled random walk in a simplified way instead of a
list of possibly many adapted symmetric sample random walks as it is the case
with function [adaptedSampledRandomWalkGenerator][adaptedsampledrandomwalkgenerator].

The returned value is simplified because it does not return an list of random walk
but instead it returns a uniq data.frame containing a symmetric random walk along
with its time period values. 
