# Random Walk R package (RandomWalk)

The aim of this package is to provide a way to create and manipulate simple random walk and brownian motion  or array of them. I would be noticed that the calculation
of brownian motion is made by taking the limit of the random walk as its steps size
goes to zero. The brownian motion could therefore be read as a continously stepped
random walk.

All caluculation could be made according to their properties. Among these available:

* Expectation and variance of random walk/brownian motion
* Expectation and variance of increments
* Quadratic variation (source of the volatility computed path by path, where
probabilities is not taken into account.)

(!) Quadratic variation should be seen as the volatility term of a random walk/
brownian motion.

## Load the package

```{r load, echo=TRUE}
library(RandomWalk)
```

## Functions provided by the package

* Multiple sampled radom walk generator: [srwalkGenerator](#srwalkgenerator)
* Sampled radom walk constructor: [srwalk](#srwalk)
* Theoretical radom walk: [trwalk]
* Quadratic variation: [qvar]
* Expectation of radom walk/brownian motion: [rwexp]
* Expectation of increments: [iexp]
* Variance of radom walk/brownian motion: [rwvar]
* Variance of increments: [ivar]
 
## Description of the functions as they was created and defined

The following lines does not give example of usage of the package functions.
<!-- To get a useful bunch of way.. One can refers to "Example" folder. -->
Instead of giving such examples, they provide an brief description of the arguments 
the package functions take as well as the way these agruments are defined (along
with the default value they take)

```{r}
srwalkGenerator(steps = 100,
                prob = c('head' = .5, 'tail' = .5),
                scale = 1,
                n = 1)

srwalk(steps = 3000,
       prob = c('head' = .5, 'tail' = .5),
       scale =1)
```
  
## Functions and arguments 
 
<!-- +++++++++++++++ srwalkGenerator description +++++++++++++++ --> 
### srwalkGenerator

| Arguments | Description |
|---|---|
| time_to_maturity | Ending time up to the random walk goes |
| prob | Probability of occurence of head and tails for each step |
| scale | Define the partition of the time period. and the scale of up and down 
  factors of the random walk |
| n | Number of random walk generated by the function |

This function return a R *list* of multiple *data.frame*s. Each one containing
the following variables:

1. *time_period*: Ordered vector from 0 up to T(time_to_maturity). It represents 
  the time period in which the random walk evolved. The partition of this vector
  depends on the variable *scale*.
2. *random_walk_path*: All random values taken by the sampled random walk.  

#### Example of usage

```{r}
library(RandomWalk)
# The following line set the variable @sampled with a list of 20
# data.frame of Adapted random walk.
Sampled <- srwalkGenerator(steps = 500, n = 20)
```

<!-- +++++++++++++++ srwalk description +++++++++++++++ --> 
### srwalk
 
| Arguments | Description |
|---|---|
| time_to_maturity | Ending time up to the random walk goes |
| prob | Probability of occurence of head and tails for each step |
| scale | Define the partition of the time period. and the scale of up and down 
  factors of the random walk |
  
This function can be used as a constructor of a unique random walk.
It returns a unique S3 object whose class is c("data.frame", "randomwalk")

The specificity of the class "randomwalk" will be useful for the created
generic methods to pick the correct function.
  
The returned value is simplified in a way that it is not a list of random walks
but instead it returns a uniq *data.frame* containing a random walk along
with its time period values. 

#### Example of usage
  
```{r}
library(RandomWalk)
# The following line set the variable @sampled with a list of 20
# data.frame of Adapted random walk.
Sampled <- srwalk(steps = 500, n = 20)
``` 
