# Random Walk R package (RandomWalk)

The aim of this package is to provide a way to create and manipulate simple random walk  or array of random walks. 
Caluculation could be made according to their properties. Among these available:

* Expectation and variance of random walk
* Expectation and variance of increments
* Quadratic variation (source of the volatility computed path by path)

From Theory, the quadratic variation would alway be computed on unique path. Whereas
the variance would be either empirical, that means related to several
path of random walks or theoretical, based on the distribution of all the possible
values taken by the random walk up to time T.

## Load the package

```{r load, echo=TRUE}
library(RandomWalk)
```


## Functions provided by the package

* [adaptedSampledRandomWalkGenerator](#adaptedsampledrandomwalkgenerator)
* [adaptedSampledRandomWalk](#adaptedsampledrandomwalk)
* [sampleRandomWalk](#samplerandomwalk)
* [sampleRandomWalkGenerator](#samplerandomwalkgenerator)

## Description as being created and defined

The following lines does not give example of usage of the package functions.
Instead it provides an brief descriptions of their arguments
along with the default value they take.

```{r}
adaptedSampledRandomWalkGenerator(steps = 3000,
                                  prob = c('head' = .5, 'tail' = .5),
                                  n = 1)

adaptedSampledRandomWalk(steps = 3000,
                         prob = c('head' = .5, 'tail' = .5))

sampleRandomWalkGenerator(steps = 3000,
                          prob = c('head' = .5, 'tail' = .5),
                          n = 1)

sampleRandomWalk(steps = 3000,
                 prob = c('head' = .5, 'tail' = .5),
                 n = 1)
```
  

## Functions and arguments

 
### adaptedSampledRandomWalkGenerator

 | Arguments | Description |
|---|---|
| steps | Number of steps of the random walk |
| prob | Probability of occurence of head and tails for each step |
| n | Number of random walk generated by the function |

This function return a R [list](https://www.rdocumentation.org/packages/base/versions/3.4.1/topics/list)
of [data.frame](https://www.rdocumentation.org/packages/base/versions/3.4.1/topics/data.frame) containing:

1. *x axis*: Ordered vector from 0 up to T. It represents the time period in which the random walk evolved.
2. *y axis*: All random values taken by the symmetric sampled random walk. This variable depends on the time
independent non-random variable

#### Example of usage of adaptedSampledRandomWalkGenerator function:

```{r}
library(RandomWalk)
# The following line set the variable @sampled with a list of 20
# data.frame of Adapted random walk.
Sampled <- adaptedSampledRandomWalkGenerator(steps = 500, n = 20)
```

### adaptedSampledRandomWalk

| Arguments | Description |
|---|---|
| steps | Number of steps of the random walk |
| prob | Probability of occurence of head and tails for each step |

It return a unique adapted sampled random walk in a simplified way instead of a
list of possibly many adapted symmetric sample random walks as it is the case
with function [adaptedSampledRandomWalkGenerator][adaptedsampledrandomwalkgenerator].

The returned value is simplified because it does not return an list of random walk
but instead it returns a uniq data.frame containing a symmetric random walk along
with its time period values.

### sampleRandomWalkGenerator

| Argument | Description |
|---|---|
| steps | Number of steps of the random walk |
| prob | Probability of occurence of head and tails for each step |
| n | Number of random walk generated by the function |

### sampleRandomWalk

| Argument | Description |
|---|---|
| steps | Number of steps of the random walk |
| prob | Probability of occurence of head and tails for each step |

