# Random Walk R package (RandomWalk)

The aim of this package is to provide a way to create and manipulate simple random walk  or array of random walks. 
Caluculation could be made according to their properties. Among these available:

* Expectation and variance of random walk
* Expectation and variance of increments
* Quadratic variation (source of the volatility computed path by path)

From Theory, the quadratic variation would alway be computed on unique path. Whereas
the variance would be either empirical, that means related to several
path of random walks or theoretical, based on the distribution of all the possible
values taken by the random walk up to time T.

## Load the package

```{r load, echo=TRUE}
library(RandomWalk)
```


## Functions provided by the package

* [adaptedSampledRandomWalkGenerator](#adaptedsampledrandomwalkgenerator)
* [adaptedSampledRandomWalk](#adaptedSampledRandomWalk)
* [sampleRandomWalk](#sampleRandomWalk)
* [sampleRandomWalkGenerator](#sampleRandomWalkGenerator)

## Description as being created and defined

The following lines does not give example of usage of the package functions.
Instead it provides an brief descriptions of their arguments
along with the default value they take.

```{r}
adaptedSampledRandomWalkGenerator(steps = 3000,
                                  prob = c('head' = .5, 'tail' = .5),
                                  n = 1)

adaptedSampledRandomWalk(steps = 3000,
                         prob = c('head' = .5, 'tail' = .5))

sampleRandomWalkGenerator(steps = 3000,
                          prob = c('head' = .5, 'tail' = .5),
                          n = 1)

sampleRandomWalk(steps = 3000,
                 prob = c('head' = .5, 'tail' = .5),
                 n = 1)
```
  

## Functions and arguments

 
### adaptedSampledRandomWalkGenerator

Function that return a list of data.frame. Each data.frame contains two variables. 

The first one is the x label (which correspond to the index of the adapted 
filtration)

The second column is a sampled symmetric random walk.
There are as many path as the value of argument **n**. 

For instance the following code: 

```{r}
library(RandomWalk)
adaptedSampledRandomWalkGenerator(steps = 500, n = 20)
```

will generate a list of **20** random walks along with the index of each step.

| Argument | Description |
|---|---|
| steps | Number of steps of the random walk |
| prob | Probability of occurence of head and tails for each step |
| n | Number of random walk generated by the function |

### adaptedSampledRandomWalk

| Argument | Description |
|---|---|
| steps | Number of steps of the random walk |
| prob | Probability of occurence of head and tails for each step |

### sampleRandomWalkGenerator

| Argument | Description |
|---|---|
| steps | Number of steps of the random walk |
| prob | Probability of occurence of head and tails for each step |
| n | Number of random walk generated by the function |

### sampleRandomWalk

| Argument | Description |
|---|---|
| steps | Number of steps of the random walk |
| prob | Probability of occurence of head and tails for each step |

