---
output:
  md_document: default
  pdf_document:
    smart: false
  html_document:
    smart: false 
---
# Random Walk R package (RandomWalk)

## Introduction

The aim of this package is to provide a way to create and manipulate discrete 
random walk and brownian motion or list of them. It would be noticed that the construction
of brownian motion is made by taking the limit of the random walk as its step size
goes to zero. The brownian motion could therefore be read as a continously stepped
random walk.

By convention the step size of a random walk (with no scale defined) is 1.
It means that at each time step the value of the random walk is likely to be
the former one plus or minus 1.
Moreover the step size of a Scaled Random Walk is defined by the following formula:
1/sqrt(scale) = sqrt(scale)^(-1).
In contrast of the Random Walk, the Brownian Motion has no natural computed step.
Each value taken by its increments, from time t_k to t_l (with k < l) is randomly 
calculated using the Normal Law with mean 0 and variance(t_l - t_k).

As previously mentioned all caluculation could be made according to their properties. Among these available:

* Expectation and variance of random walk/brownian motion
* Expectation and variance of increments
* Quadratic variation (source of the volatility computed path by path, where
probabilities is not taken into account.)

(!) Quadratic variation can be thought as the volatility term of a random walk/
brownian motion. Even if the special case of Brownian Motion and Random Walk
incurs the same Quadratic Variation among all the different path.

### Notes

**For more technical information and example of usage** of the RandomWalk package, 
please feel free to have a look inside the [vignettes](/vignettes) repository.


<!-- +++++++++++++++ New H2 +++++++++++++++ -->


## Functions provided by the package

* Multiple Sampled Radom Walks generator: [srwalkGenerator](#srwalkgenerator)
* Sampled Radom Walk constructor: [srwalk](#srwalk)
* Theoretical Radom Walk: [trwalk](#trwalk)
* Multiple Brownian Motions generator: [sbmotionGenerator](#sbmotiongenerator)
* Brownian Motion constructor: [sbmotion](#sbmotion)
* Theoretical Radom Walk: [tbmotion]()
* Quadratic Variation: [qvar](#qvar)


<!-- +++++++++++++++ New h2 +++++++++++++++ --> 

 
## Description of the functions as they was created and defined

The following lines does not fully give a set of examples of usage 
of the package functions.
<!-- To get a useful bunch of that.. One can refers to "Example" folder. -->
Instead of giving such examples, they provide an brief description of the arguments 
the package functions take as well as the way these agruments are defined (along
with the default value they take)

 
 
### srwalkGenerator


#### Definition

| Arguments | Default | Description |
|---|---|---|
| time_to_maturity | 100 | Final time up to the random walk goes |
| prob | 0.5 | Probability of occurence of head and tail for each step |
| scale | 1 | Define the partition of the time period. and the scale of up and down factors of the random walk, following the rule: sqrt(scale)^(-1)|
| seed | 1 | The seed fixes initial value of the pseudo random number generation |
| n | 1 | Number of random walk generated by the function |

This function return a R *list* of multiple *data.frame*s. Each one contains
the following variables:

1. *time_period*: Ordered vector from 0 up to T(time_to_maturity). It represents 
  the time period in which the random walk evolved. The partition step of this vector
  depends on the variable *scale*.
2. *random_walk_path*: All random values taken by the sampled random walk.  



#### Example of usage

```{r}
library(RandomWalk)
# The following line set the variable @sampled with a list of 20
# data.frame of Adapted random walk.
Sampled <- srwalkGenerator(time_to_maturity = 500, n = 20)
```

  

<!-- +++++++++++++++ srwalk description +++++++++++++++ --> 
### srwalk
 
| Arguments | Default | Description |
|---|---|---|
| time_to_maturity | 100 | Final time up to the random walk goes |
| prob | 0.5 | Probability of occurence of head and tail for each step |
| scale | 1 | Define the partition of the time period. and the scale of up and down factors of the random walk, following the rule: sqrt(scale)^(-1)|
| seed | 1 | The seed fixes initial value of the pseudo random number generation |
  
This function is defined to be the constructor of a unique Sampled Random Walk.
It returns a uniq S3 object with classes as follow:

```{R}
c("sampled_randomwalk", "data.frame")
print('coucou')
```
 
srwalk() output a data.frame which contains each step of the time value along 
with the associated Sampled Random Walk value.



#### Example of usage
  
```{r}
library(knitr)
library(RandomWalk)
# Generate a 150 steps symmetric random walk
srw <- srwalk(time_to_maturity =  150)
kable(head(srw))
``` 




